Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Update results

```{r load}
library(sf)
library(tidyverse)
library(tmap)
u = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rsf_leeds.Rds"
r_original = readRDS(url(u))
ur = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rtid.csv"
rtid = readr::read_csv(ur)
# uh = "http://media.nhschoices.nhs.uk/data/foi/Hospital.csv"
# download.file(uh, "uh.csv")
h = readr::read_delim("uh-edited.csv", delim = "|")
# nrow(h) # 1221 hospitals
h_clean = h %>% 
  mutate(Longitude = as.numeric(Longitude)) %>% 
  mutate(Latitude = as.numeric(Latitude)) %>% 
  filter(!is.na(Longitude)) %>% 
  filter(!is.na(Latitude))
hsf = h_clean %>% st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
region = ukboundaries::leeds
```

```{r parameters}
min_cycling_potential = 0
min_grouped_cycling_potential = 100
min_grouped_length = 600
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
key_destination_buffer_radius = 5000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
h_leeds = hsf[city_centre_buffer, ]
h_leeds_buffer = stplanr::geo_buffer(h_leeds, dist = key_destination_buffer_radius)
city_key_buffer = st_union(city_centre_buffer, st_union(h_leeds_buffer))
```

@@

touching_list = st_touches(r_pct_lanes_all)
g = igraph::graph.adjlist(touching_list)
components = igraph::components(g)
r_pct_lanes_all$group = components$membership
r_pct_lanes = r_pct_lanes_all %>% 
  group_by(group) %>% 
  mutate(group_length = sum(length)) %>% 
  mutate(cycling_potential_mean = mean(cycling_potential, na.rm = TRUE)) %>% 
  filter(cycling_potential_mean > min_grouped_cycling_potential)
r_pct_lanes = r_pct_lanes %>% filter(group_length > min_grouped_length)

@@

## Scenarios and visualisation

To make the results more accessible and actionable...

@@

We found that...

@@

>>>>

```{r load}
library(sf)
library(tidyverse)
library(tmap)
if(!file.exists("rsf_leeds.Rds")) {
  u = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rsf_leeds.Rds"
  download.file(u, "rsf_leeds.Rds")
}
r_original = readRDS("rsf_leeds.Rds")
if(!file.exists("rtid.csv")) {
  ur = "https://github.com/cyipt/tempCycleways/releases/download/0.1/rtid.csv"
  download.file(ur, "rtid.csv")
}
rtid = readr::read_csv("rtid.csv")
# uh = "http://media.nhschoices.nhs.uk/data/foi/Hospital.csv"
# download.file(uh, "uh.csv")
h = readr::read_delim("uh-edited.csv", delim = "|")
# nrow(h) # 1221 hospitals
h_clean = h %>% 
  mutate(Longitude = as.numeric(Longitude)) %>% 
  mutate(Latitude = as.numeric(Latitude)) %>% 
  filter(!is.na(Longitude)) %>% 
  filter(!is.na(Latitude))
hsf = h_clean %>% st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326)
region = ukboundaries::leeds
tmap_mode("plot")
```

```{r parameters}
regexclude = "welling"
min_cycling_potential = 0
min_grouped_cycling_potential = 100
min_grouped_length = 500
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
key_destination_buffer_radius = 5000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
h_leeds = hsf[city_centre_buffer, ]
h_leeds_buffer = stplanr::geo_buffer(h_leeds, dist = key_destination_buffer_radius)
city_key_buffer = st_union(city_centre_buffer, st_union(h_leeds_buffer))
```

@@

touching_list = st_touches(r_pct_lanes_all)
g = igraph::graph.adjlist(touching_list)
components = igraph::components(g)
r_pct_lanes_all$group = components$membership
r_pct_lanes = r_pct_lanes_all %>% 
  group_by(group) %>% 
  mutate(group_length = sum(length)) %>% 
  mutate(cycling_potential_mean = weighted.mean(cycling_potential, w = length, na.rm = TRUE)) %>% 
  filter(cycling_potential_mean > min_grouped_cycling_potential)
r_pct_lanes = r_pct_lanes %>% filter(group_length > min_grouped_length)

@@

```{r joining}
r_pct_grouped = r_pct_lanes %>%
  group_by(name, group) %>%
  summarise(
    group_length = sum(length),
    cycling_potential = round(weighted.mean(cycling_potential_mean, length))
  )
# summary(r_pct_grouped$group_length)
r_pct_top = r_pct_grouped %>%
  filter(group_length > min_grouped_length) %>% 
  filter(cycling_potential > min_grouped_cycling_potential) %>% 
  filter(!grepl(pattern = regexclude, name, ignore.case = TRUE)) %>% 
  mutate(kkm_cycled = round(cycling_potential * group_length / 1000))
# head(r_pct_top$kkm_cycled)

r_pct_lanes_overlap = r_pct_lanes[r_pct_top, , op = sf::st_covered_by] # works
# r_pct_no_overlap = st_difference(r_pct_lanes, r_pct_top) # slow
r_pct_no_overlap = r_pct_lanes %>% 
  filter(!idGlobal %in% r_pct_lanes_overlap$idGlobal)

r_pct_top_n = r_pct_top %>% 
  group_by(name) %>% 
  slice(which.max(kkm_cycled)) %>% 
  filter(name != "") %>% 
  ungroup() %>% 
  top_n(10, wt = kkm_cycled) 
# aim: make the labels go on the longest sections
# %>% 
#   st_cast("LINESTRING") %>% 
#   mutate(length_section = as.numeric(st_length(.))) %>% 
#   group_by(name) %>% 
#   slice(which.max(length_section))
# r_pct_top_n$name
# summary(r_pct_grouped$group_length)
```

<!-- ## Scenarios and visualisation -->

<!-- To make the results more accessible and actionable we have made the results, discussed in the next section, publicly available at  -->

@@

```{r res, fig.cap="Results, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled."}
tmap_mode("view")
tm_shape(r_pct_no_overlap) + tm_lines(col = "lightblue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top) + tm_lines(col = "blue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top_n) + tm_text("name")
```

```{r}

```

@@

# References
